---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# getnews

<!-- badges: start -->
<!-- badges: end -->

The goal of `{getnews}` is to obtain all the NEWS items that concern a particular function. This can be used to know when a particular function was introduced in a package, but also when the behavior of a function changed, when it gained or lost arguments, etc. This should be particularly helpful to package developers who want to check if introducing a particular function will break backwards compatibility.

## Installation

You can install the development version of `{getnews}` from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("etiennebacher/getnews")
```

## Example

```{r example}
library(getnews)

getnews("paste0")

getnews("relocate", "dplyr")

getnews("testServer", "shiny", recent_first = FALSE)
```
